Sampling-based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
added rrtdyn9

\begin{figure}
\centering
{
\renewcommand{\tabcolsep}{1pt}
\begin{tabular}{cccccc}
\includegraphics[width=0.19\textwidth]{fig/rrtdyn2} &
\includegraphics[width=0.19\textwidth]{fig/rrtdyn3} &
\includegraphics[width=0.19\textwidth]{fig/rrtdyn4} & 
\includegraphics[width=0.19\textwidth]{fig/rrtdyn6} &
\includegraphics[width=0.19\textwidth]{fig/rrtdyn7} \\
 frame $i$ & frame $i+1$ & frame $i+1$ & frame $i+1$ & frame $i+1$ \\
void space & pruning & after pruning & void space  & merging \\
           &          &                & detection\\
\multicolumn{5}{c}{\includegraphics[width=0.4\textwidth]{fig/rrtdyn8}} \\
\multicolumn{5}{c}{ frame $i$ \hskip 28pt frame $i+1$ }
\end{tabular}
}
\caption{\label{fig::transfer}
Tree transfer, merging and graph of relations.
In the frame $i$, the void space consists of one component $C_0$ (nodes 1--7).
After the pruning, the nodes leading to collisions with atoms are removed (nodes $5,6$).
The parents of the remaining nodes are set to the same nodes in the previous frame, e.g., parent of node 3 in frame $i+1$ is the node 3 in the frame $i$.
The tree is then again expanded in the new frame (green nodes).
After merging, two components can be identified ($C_1$ and $C_2$). 
Since some of the nodes of these components point to the previous frame (the red nodes),
      both components $C_1$ and $C_2$ are connected to $C_0$.
}
\end{figure}

>>>>

\begin{figure}
\centering
{
\renewcommand{\tabcolsep}{1pt}
\begin{tabular}{cccccc}
\includegraphics[width=0.19\textwidth]{fig/rrtdyn2} &
\includegraphics[width=0.19\textwidth]{fig/rrtdyn3} &
\includegraphics[width=0.19\textwidth]{fig/rrtdyn4} & 
\includegraphics[width=0.19\textwidth]{fig/rrtdyn6} &
\includegraphics[width=0.19\textwidth]{fig/rrtdyn7} \\
 frame $i$ & frame $i+1$ & frame $i+1$ & frame $i+1$ & frame $i+1$ \\
void space & pruning & after pruning & void space  & merging \\
           &          &                & detection\\
& \multicolumn{3}{c}{\includegraphics[width=0.4\textwidth]{fig/rrtdyn8}} & \includegraphics[width=0.19\textwidth]{fig/rrtdyn9} \\
&  \multicolumn{3}{c}{ frame $i$ \hskip 28pt frame $i+1$ } & graph of components
\end{tabular}
}
\caption{\label{fig::transfer}
Tree transfer, merging and graph of relations.
In the frame $i$, the void space consists of one component $C_0$ (nodes 1--7).
After the pruning, the nodes leading to collisions with atoms are removed (nodes $5,6$).
The parents of the remaining nodes are set to the same nodes in the previous frame, e.g., parent of node 3 in frame $i+1$ is the node 3 in the frame $i$.
The tree is then again expanded in the new frame (green nodes).
After merging, two components can be identified ($C_1$ and $C_2$). 
Since some of the nodes of these components point to the previous frame (the red nodes),
      both components $C_1$ and $C_2$ are connected to $C_0$.
}
\end{figure}
